\documentclass[10pt,a4paper]{article}

\usepackage{fontspec}
\usepackage[top=1cm]{geometry}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Ligatures={Common},Numbers={Lining}]{Linux Libertine}
\author{Michal Staniaszek}
\title{My Information}

\begin{document}
\maketitle

\begin{enumerate}
\item I studied my BSc in Computer Science at the University of Birmingham in
  the UK, spending one year at Keio University in Tokyo. Now studying Systems,
  Control and Robotics at KTH following the Robotics and Autonomous Systems
  track as an international masters student.
\item I have Machine Learning this period and Machine Learning Advanced Course
  next period. I'm not sure exactly how much work each of those is, but I should
  be available to do as much work as is necessary.
\item My best quality for teamwork is my willingness to work a lot to make sure
  that they work as intended (or at least close enough).
\item My worst quality for teamwork is my perfectionism in terms of code
  structure and so on. I like for code to look nice and I often spend too much
  time on this instead of implementing stuff that just works. I'm not sure if
  this is good or bad.
\item The part of the project that is most interesting to me is probably
  the programming part. In particular I want to try and do things so that it's
  easier to integrate all of the different modules at the end of the project.
\item Cycling, watching stuff on YouTube, reading (SciFi), computer games, music
  (post-rock, modern classical)

\end{enumerate}

\end{document}